Bayesian regression facilitates quantitative modelling of cell metabolism

### 2023-10-31 paper/main.qmd

Results of removing concentration measurements for the metabolite $ahcys_c$
from our case study dataset.  (**Top**) A comparison of metabolite concentration
residuals between the full measurement dataset (blue-green) and the missing-data
dataset (grey), displayed on natural logarithmic scale. The missing-data
model was unable to predict the withheld $ahcys_c$ concentrations.  (**Bottom
Left**) The marginal posterior distribution for the Michaelis constant
$K_m^{AHC1,ahcys_c}$ in each model, alongside the true parameter value used to
generate both datasets. The true value is recovered by the complete-data model
but not by the missing-data model.  (**Bottom Right**) The distribution of total
log-likelihood for out-of-sample flux measurements in both models. There is a
significant overlap between the two distributions, suggesting that removing the
$ahcys_c$ measurement did not cause catastrophic prediction failure. However,
overall the complete-data model tended to make better predictions.

>>>>

Marginal posterior distributions from our main model run. (**Top left**)
Comparison of posterior predictive intervals with simulated flux measurement
values. All the flux measurements are within the predictive intervals,
indicating a good fit. (**Top right**) Comparison of posterior predictive
intervals with simulated concentration measurement values. These also show a
good fit. (**Bottom left**) Pairwise marginal posterior distribution for two
uncorrelated parameters, namely $K_m^{AHC1,hcys-L}$ and $K_m^{AHC1_ahcys}$.
(**Bottom right**) Pairwise marginal posterior distribution for two correlated
parameters, namely $K_m^{MAT3,atp}$ and $K_{cat}^{MAT3}$.
